Changes in Faculty Composition and Stagnating State Support for Higher Education

### 2023-03-30 text/paper.tex
Finished major revision.  Needs more checks of writing style.
adjusted formatting of title page only.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Title page
% Author
\author{Senan Hogan-Hennessy \\ \vspace{0.1cm}
    Economics Department, Cornell University
}
% Title
\title{Changes in Faculty Composition and Stagnating State Support for Higher Education
    }
\date{\today\thanks{
    I thank Professor Evan Riehl for guidance on this project, Michael Lovenheim, Ronald Ehrenberg, Douglas Miller, Francine Blau, Levon Barseghyan, and Ryan Dycus for various comments on the project's direction, as well as seminar participants at Cornell University (Autumn 2022) for helpful discussion.
    This project's Github repository, with materials and (publicly available) data for replication, is available at 
    \url{https://github.com/shoganhennessy/state-faculty-composition}.
    Any comments or suggestions may be sent to me at \href{mailto:seh325@cornell.edu}{\nolinkurl{seh325@cornell.edu}}, or raised as an issue on the Github project.
    } \\ \vspace{0.1cm}
    \href{https://github.com/shoganhennessy/state-faculty-composition/blob/main/text/paper.pdf}{Newest version available here.}
}
\rhead{\today}
\lhead{Faculty Composition and State Support for Higher Education.}
% Begin
\begin{document}
\clearpage
\maketitle
\thispagestyle{empty}
% Abstract
\begin{abstract}
    \input{sections/00-abstract.tex}
\end{abstract}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Title page
% Author
\author{Senan Hogan-Hennessy \\ \vspace{0.1cm}
    Economics Department, Cornell University\thanks{
        I thank Professor Evan Riehl for guidance on this project, Michael Lovenheim, Ronald Ehrenberg, Douglas Miller, Francine Blau, Levon Barseghyan, and Ryan Dycus for various comments on the project's direction, as well as seminar participants at Cornell University (Autumn 2022) for helpful discussion.}
}
% Title
\title{Changes in Faculty Composition and Stagnating State Support for Higher Education
    }
\date{This version: \today\thanks{
    This project's Github repository, with materials and data (where publicly available) for replication, is available at 
    \url{https://github.com/shoganhennessy/state-faculty-composition}.
    Any comments or suggestions may be sent to me at \href{mailto:seh325@cornell.edu}{\nolinkurl{seh325@cornell.edu}}, or raised as an issue on the Github project.
    } \\ \vspace{0.1cm}
    \href{https://github.com/shoganhennessy/state-faculty-composition/blob/main/state-faculty-composition-2023.pdf}{Newest version available here.}
}
\rhead{\today}
\lhead{Faculty Composition and State Support for Higher Education.}
% Begin
\begin{document}
\maketitle
\thispagestyle{empty}
% Abstract
\begin{abstract}
    \input{sections/00-abstract.tex}
\end{abstract}
